%https://www.stat.berkeley.edu/~paciorek/files/cv/paciorek-cv.pdf
%https://www.stat.berkeley.edu/~paciorek/cv/cv.html

\documentclass[margin,line]{res}
\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{\small$\triangleright$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Daniel C. Posmik \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Brown University & {\it Cell:} +1 (224) 507-4045 \\ 
School of Public Health & {\it E-Mail:} \href{mailto:daniel_posmik@brown.edu}{daniel\_posmik@brown.edu} \\ 
Department of Biostatistics & {\it Google Scholar:} \href{https://scholar.google.com/citations?user=sRuEm5oAAAAJ}{user=sRuEm5oAAAAJ} \\
121 S Main St, Providence, RI 02906 & {\it Web:} \href{https://posmikdc.github.io}{posmikdc.github.io} \\       
\end{tabular}

\section{\sc Interests}
Manifold learning, geometric and shape inference, statistical network analysis, causal inference, brain imaging

\section{\sc Education}
{\bf Brown University}, Providence, Rhode Island USA\\
\vspace*{-.15in}
\begin{list1}
  \item[] Ph.D., Biostatistics \hfill Exp. May 2029

\begin{list1}
\vspace*{.05in}
\item[\cdot] Advisor: Prof. \href{http://www.anieloyan.com}{Ani Eloyan}
\end{list1}
\vspace*{.03in}
\item[] Sc.M., Biostatistics (Concurrent) \hfill Exp. May 2026
\end{list1}

{\bf University of Chicago}, Chicago, Illinois USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.15in}
\begin{list1}
\item[] Graduate Student at Large (Statistics) \hfill May 2024
\end{list1}

{\bf University of Cincinnati}, Cincinnati, Ohio USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.15in}
\begin{list1}
\item[] B.Sc., Data Analytics; B.B.A., Economics; Mathematics Minor \hfill May 2022
\item[] A.A., Business Administration \hfill May 2020
\end{list1}


\section{\sc Honors and Awards} 
McCall MacBain Finalist Award (Deferred for Ph.D.) (80 out of 1,000+ applicants) \hfill 2023 \\  
Presidential Leadership Medal of Excellence (Univ. of Cinci) (4 yearly recipients) \hfill 2022 \\ 
Non-Traditional Student of the Year (Univ. of Cinci)(1 yearly recipient) \hfill 2022 \\
Annie Fitzgerald Community Service (Univ. of Cinci) Award (2 yearly recipients) \hfill 2021


\section{\sc Peer-Reviewed Publications}
{\bf Posmik, D.C.} 2022. \href{https://ir.library.louisville.edu/jsfa/vol51/iss3/4/}{Predicting International Student Enrollment by Institutional Aid: A Random and Fixed Effects Approach}. Journal of Student Financial Aid, 51 (3), Article 4.  


\section{\sc Academic Experience}
{\bf Brown University}, Providence, Rhode Island USA

\vspace{-.3cm}
{\em Graduate Student} \hfill {Aug. 2024{ \textemdash } Present} \\ 
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Current Ph.D.~research; Ph.D.~and Masters level coursework. 
\end{list1}

{\bf University of Chicago}, Chicago, Illinois USA

\vspace{-.3cm}
{\em Research Assistant, Department of Comparative Human Development} \hfill {Jan.{ \textemdash } May 2024} \\ 
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Assisted \href{https://voices.uchicago.edu/ghong/}{Prof. Guanglei Hong} with methods development in causal decomposition analysis
\item[\cdot] Studied causal identification in cumulative treatment setting, applied to K-12 education data
\end{list1}

\vspace{-.3cm}
{\em Community Data Fellow, Data Science Institute} \hfill {Sept.{ \textemdash } Dec. 2023} \\ 
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Developed an interactive Tableau dashboard for the State of Illinois' Commission on Equity and Inclusion, visualizing impact metrics of the {\em Business Enterprise Program}
\end{list1}

\vspace{-.3cm}
{\em Project Associate, Energy \& Environment Lab} \hfill {Jan.{ \textemdash } June 2023} \\ 
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Coordinated an RCT on the effect of agricultural machinery on illegal burning of crop residue
\item[\cdot] Processed and modeled environmental remote sensing data; assisted with grant updates, reports, and field team coordination
\end{list1}

%\section{\sc Papers in preparation}

%Ventura, V., C.J. Paciorek, and J.S. Risbey.  Controlling the proportion of falsely-rejected hypotheses when conducting multiple tests with geophysical data.

%Ickes, K., C.J. Paciorek, and S. Thomas.  Effects of wild pigs on forest demographic processes in Malaysia.

\section{\sc Presentations and Talks}
Conference Presentations:
\begin{list1}
\item[\cdot] "Predicting International Student Enrollment by Institutional Aid: A Random and Fixed Effects Approach" (2022) Presented at the Economic Scholars Conference (Cleveland Federal Reserve), Cleveland, Ohio, USA
\end{list1}

Miscellaneous:
\begin{list1}
\item[\cdot] "Telling Stories with Data" (2021). Gave TEDx talk. TEDxUCincinnati, Cincinnati, Ohio, USA 
\end{list1}

%Paciorek, C.J. and R. Rosenfeld.  2000.  Minimum classification error training in exponential language models.  2000 Spring Transcription Workshop, College Park, Maryland.
%\vspace*{-.25in}  
%\begin{verbatim}http://www.nist.gov/speech/publications/tw00/html/abstract.htm#cp1-50\end{verbatim}

\section{\sc Industry Experience}
{\bf The Brattle Group}, Boston, Massachusetts USA

\vspace{-.3cm}
{\em Research Analyst} \hfill {June{ \textemdash } Dec. 2022}\\
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Supported the electricity practice group, conducting analyses in wholesale energy markets, regulatory policy, and congestion patterns. 
\end{list1}

\section{\sc Community Service}
{\bf The Neo Initiative}, Cincinnati, Ohio USA

\vspace{-.3cm}
{\em President and Founder} \hfill {March 2020 { \textemdash } May 2022} \\
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Served 15 black-owned small businesses with pro-bono consulting services in data analytics
\item[\cdot] Hosted a virtual state-sponsored data literacy series, reaching 300+ minority-owned businesses
\end{list1}

\section{\sc Teaching Experience}
{\bf University of Chicago}, Chicago, Illinois USA

\vspace{-.3cm}
{\em Teaching Assistant, Econometrics (ECON21020)} \hfill {Jan.{ \textemdash } May 2024}\\
\vspace{-.4cm}
\begin{list1}
\item[\cdot] Shared responsibility for grading, office hours, and leading discussion sections for approximately 40 students
\end{list1}


\section{\sc Technical \\ Skills} 
%\begin{list2}
Languages: R, Python, limited exposure to Julia \\
Machine Learning: Keras \\ 
Data Wrangling: SQL, Selenium \\
Operating Systems:  UNIX/Linux, Windows, MacOS \\
Miscellaneous: \LaTeX, Lua, Git, Microsoft Office
%\end{list2}

\section{\sc Professional Service} 
Journal and Proposal Reviewer:
\begin{list1}
\item[\cdot] 2022: Journal of Student Financial Aid
\end{list1}

\end{resume}

% display today's date as Month Year after a vertical space below the end of the text
\begin{center}
  \vfill
  Last Updated \today
\end{center}

\end{document}
